---
title: Sample
subtitle: p-value
author: Bansari Kathrotia
date: 4/5/2024
toc: true
---

```{r}
#| message: false
#| echo: false

library(tidyverse)
```

# Section 1: Basic test formatting
## Sub-section
### Header

- some
- word
- in
- bullets

1. some
2. numbers
3. in 
4. a 
5. list

text can be **bold**, or _italics_, or ~~strikethrough~~

My website is <https://rsm-bkathrotia.github.io/bkathrotia.github.io/> or [here](https://rsm-bkathrotia.github.io/bkathrotia.github.io/)

# Section 2: some Math

If you want inline $y = mx + b$

$$
\int_0^1 x^2 dx = \frac{1}{3} \hspace{2em} \beta \hspace{2em} \text{or} \hspace{2em} \hat{\beta}
$$

some latex math:

```{=latex}
\begin{align}
y &= a(b+c) \\
  &= ab + ac
\end{align}
```

# Section 3: code

You can do inline code like so `r format(sqrt(2), digits = 3)`

```{r}
#| eval: false
data(mtcars)
cor(mtcars$mpg, mtcars$wt)
```

# Section 4: Plots


```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: center

p <- mtcars |>
    ggplot(aes(mpg, wt)) +
    geom_point(col = "dodgerblue4", size = 2)
print(p)
```

# Section 5: Tables
```{r}
mtcars[1:5, ]
```


```{r}
knitr :: kable(mtcars[1:5, ],)
```

# Bonus Section 

:::{.callout-note}
### Note title

note body

:::

a tabset panel

:::{.panel-tabset}

## Jesus

```{r}
#| echo: false
p
```
## Brian

```{r}
#| echo: false
#| message: false
#| 
p + geom_smooth(method = "lm", se = F)
```
:::